---
title: "PA1_template"
author: "Me"
date: "6/11/2020"
output: html_document
---

# 1 Code for reading in the dataset and/or processing the data

```{r}
setwd("C:/Allen/Training/Coursera/Data Science/ReproducibleResearch")
data<-read.csv("activity.csv")
```

# 2 Histogram of the total number of steps taken each day
```{r}
data$date<-as.Date(data$date)

sum_steps<-aggregate(data$steps,by=list(data$date),FUN=sum,na.rm=TRUE) 

hist(sum_steps$x, 
     breaks=seq(from=0, to=25000, by=2500),
     col="Green", 
     xlab="Total # of steps", 
     ylim=c(0, 20), 
     main="Histogram of the total # of steps taken each day\n(NA removed)")
```

# 3 Mean and median number of steps taken each day

```{r}
mean(sum_steps$x)
median(sum_steps$x)
```

# 4 Time series plot of the average number of steps taken

```{r}
avg_steps<-aggregate(data$steps,by=list(data$interval),FUN=mean,na.rm=TRUE)
colnames(avg_steps)<-c("interval","steps")
library(ggplot2)
ggplot(aes(x=interval,y=steps),data=avg_steps)+geom_line()
```

# 5 The 5-minute interval that, on average, contains the maximum number of steps

```{r}
avg_steps[avg_steps$steps==max(avg_steps$steps),1]
```

# 6 Code to describe and show a strategy for imputing missing data

```{r}
sum(is.na(data$steps))
data$steps[is.na(data$steps)]<-mean(data$steps,na.rm=TRUE)
```

# 7 Histogram of the total number of steps taken each day after missing values are imputed

```{r}
sum_steps<-aggregate(data$steps,by=list(data$date),FUN=sum,na.rm=TRUE) 

hist(sum_steps$x, 
     breaks=seq(from=0, to=25000, by=2500),
     col="green", 
     xlab="Total # of steps", 
     ylim=c(0, 30), 
     main="Total # of steps taken each day\n(NA replaced by mean)")

mean(sum_steps$x)
median(sum_steps$x)
```

# 8 Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}

# Convert to weekdays

data$days=tolower(weekdays(data$date))

# days weekend and weekdays

data$day_type<-ifelse(data$days=="saturday"|data$days=="sunday","weekend","weekday")

#mean steps taken on weekend or weekday in the intervals

avg_steps<-aggregate(data$steps,by=list(data$interval,data$day_type),FUN=mean,na.rm=TRUE)

colnames(avg_steps)<-c("interval","day_type","steps")

# Create panel plot between average steps and interval seperated by day type

ggplot(aes(x=interval,y=steps),data=avg_steps)+geom_line()+facet_wrap(~avg_steps$day_type)
```


